---
title: "Walkthrough guides analysis"
date: "July 20th 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

### 

Presented below is an analysis of walkthrough guides. 
This document summarizes the guides analysis so far in https://docs.google.com/document/d/17NBbp5bq3NbxsemQVWa19DyI2aksfaeA1rECalguksg/edit#

###

```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = "/Users/sukmanilamba/Downloads")
knitr::opts_chunk$set(echo = TRUE)
# Required libraries
library(dplyr)
library(lubridate)
library(anytime)
library(tidyr)
library(reshape2)
library(leaps)
library(caret)
library(rpart)
library(data.table)
library(boot)
library(ggplot2)
library(ggthemes)
library(plotly)
library(shiny)

```

```{r,echo=FALSE}

setwd("/Users/sukmanilamba/Downloads")
dfN <- read.csv("GuideEvents_Combined.csv")
GL <- read.csv("updated_guides_list.csv")
dfN1 <- merge(dfN,GL,by=c('guideId','guideStepId'))
dfNU <- dfN1
dfNU <- subset(dfNU,!(is.na(dfNU$numSteps)))
factor_not <- c("guideType","type","guideId","visitorId","accountId","state")
dfNU[,factor_not] <- sapply(dfNU[,factor_not],as.character)
dfNU <- subset(dfNU,state == 'public')
dfNU <- subset(dfNU,dfNU$numSteps >= 2) # Guides with more than 1 step
dfNU$browserTime <- as.numeric(dfNU$browserTime)/1000 #to seconds
dfNU$browserTime <- as.POSIXct((dfNU$browserTime),origin="1970-01-01") #to date time stamp
numrows <- length(unique(dfNU$guideId))
### Setting up dataframes to collect in all the relevant results

numcols <- max(dfNU$numSteps) + 5 # This is because the first two columns have the guide id and total number of visitors
numvis <- length(unique(dfNU$visitorId))
#numcolvis <- max(dfNU$numSteps)+5 # WHY DID YOU CREATE THIS?

NBuckets <- as.data.frame(matrix(0.0,numrows,numcols)) # guide level
NVBuckets <- as.data.frame(matrix(0.0,numvis,numcols)) # Visitor level
NCBuckets <- as.data.frame(matrix(0.0,numrows,numcols)) # guide level
colnames(NBuckets) <- c("All_Guides","All_Visitors","Num_Steps","Segment","Completed")
colnames(NCBuckets) <- c("All_Guides","All_Visitors","Num_Steps","Segment")
colnames(NVBuckets) <- c("Guide","Visitor","Num_Steps","Segment","Completed")

guidelist <- unique(dfNU$guideId)

NBuckets$All_Guides <- guidelist
NCBuckets$All_Guides <- guidelist

NVBuckets$Visitor <- unique(dfNU$visitorId)
```

```{r,echo=FALSE}
# Initializing the analysis with the dataframes
for (i in 1:numrows) # For all of the guides
{
  r1 = NBuckets$All_Guides[i];
  dfr1 = subset(dfNU,guideId == r1)
  NBuckets$All_Visitors[i] = length(unique(dfr1$visitorId))
  NBuckets$Num_Steps[i] = dfr1$numSteps[1]
  NBuckets$Segment[i] = dfr1$segmentId[1]
  
  NCBuckets$All_Visitors[i] = length(unique(dfr1$visitorId))
  NCBuckets$Num_Steps[i] = dfr1$numSteps[1]
  NCBuckets$Segment[i] = dfr1$segmentId[1]
  
}


# Extracting the number of users who completed every step for each guide

for (i in 1:numrows)
{
  
  r1 = NBuckets$All_Guides[i]
  dfr1 = subset(dfNU,guideId == r1)
  nsteps = NBuckets$Num_Steps[i]
  nstepval = nsteps - 1
  
  sdfrf = subset(dfr1,stepIndex == nstepval) # The final step of the walkthrough
  sdfrf = subset(sdfrf,type == 'guideSeen')
  
  FC = dim(sdfrf)[1]
  if (FC > 0)
  {
    NBuckets$Completed[i]  = length(unique(sdfrf$visitorId));
    # This vector tells us whether any visitors of this guide actually completed it,
    # as this is the set of those who went through the final step of the walkthrough.
  }
  
  
  for (j in 1:nsteps)
  {
    val = j-1
    sdfr1 = subset(dfr1,stepIndex == val)
    sdfr1 = subset(sdfr1,type == 'guideSeen')
    
    int_ln = length(unique(intersect(sdfr1$visitorId,sdfrf$visitorId)))
    NCBuckets[i,j+5] = int_ln;
    # What's the number of visitors who finished at this stage?
    dim1 = dim(sdfr1)
    if (dim1[1] > 0)
    {
      NBuckets[i,j+5] = length(unique(sdfr1$visitorId)) # The number of users who finished this step
    }
  }
}

NBuckets$Perc_Completed <- 100.0*(NBuckets$Completed/NBuckets$All_Visitors)

# Logic per visitor

visitorlist <- unique(dfNU$visitorId)
dfNU_GV <- dfNU[,c("guideId","visitorId")]
dfNU_GV <- dfNU_GV[!duplicated(dfNU_GV),]
numr <- dim(dfNU_GV)[1]
dfNU_GVSC <- as.data.frame(matrix(0,dim(dfNU_GV)[1],dim(dfNU_GV)[2]+8))
NVisitor <- as.data.frame(matrix(0,numr,numcols))

colnames(dfNU_GVSC) <- c("Guide","Visitor","Segment","Num_Steps","Completed","FirstStep","CompletedButOne", "StartTime","EndTime","Duration")


dfNU_GVSC$Guide <- dfNU_GV$guideId
dfNU_GVSC$Visitor <- dfNU_GV$visitorId

colnames(NVisitor) <- c("Visitor","Guide","Num_Steps","Segment","Completed")

factor_not <- c("guideId","visitorId")
dfNU_GV[,factor_not] <- sapply(dfNU_GV[,factor_not],as.character)

factor_not <- c("Guide","Visitor")
dfNU_GVSC[,factor_not] <- sapply(dfNU_GVSC[,factor_not],as.character)

numr <- dim(dfNU_GVSC)[1]

# For each visitor guide combination
for (i in 1:numr)
{
  
  
  v1 = dfNU_GVSC$Visitor[i]
  g1 = dfNU_GVSC$Guide[i]
  
  dfr1 = subset(dfNU,((visitorId == v1) & (guideId == g1)))
  dfNU_GVSC$Segment[i] = dfr1$segmentId[1]
  nsteps = dfr1$numSteps[1]
  nstepval = nsteps - 1
  dfNU_GVSC$Num_Steps[i] = nsteps
  dfr1$type <- as.character(dfr1$type)
  dfr1 = subset(dfr1,type == 'guideSeen') # We are after all only interested in the guideSeen events.
  # Future permutations should we want them
  #dfr1 = subset(dfr1,type != 'guideDismissed')
  #dfr_1 <- subset(dfr1,((stepIndex == 0) & (type == 'guideSeen')))
  #dfr_1 <- subset(dfr1,stepIndex == 0)
  dfr_1 <- subset(dfr1,stepIndex == 0)
  F0 = dim(dfr_1)[1]
  
  dfr7 <- dfr1[!is.na(dfr1$browserTime),]
  dfr10 = subset(dfr7,stepIndex == nstepval)
  FC3 = dim(dfr7)[1]
  FC10 = dim(dfr10)[1]
  
  FC10
  
  if (FC3 > 0) #Logic to read max and min time
  {
  dfNU_GVSC$StartTime[i] = min(dfr1$browserTime);
  }
  
  if(FC10 > 0)
  {
  dfNU_GVSC$EndTime[i] = min(dfr10$browserTime);
  }
  
  
  if (F0 > 0) # That this is a non-empty set or that we have complete data for this data set
  {
    dfNU_GVSC$FirstStep[i] = 1
  }
  # sdfrf = subset(dfr1,((stepIndex == nstepval) & (type == 'guideSeen')))
  penum_step = nstepval-1
  sdfrf = subset(dfr1,stepIndex == penum_step)
  sdfrf2 = subset(dfr1,stepIndex == nstepval)
  
  FC = dim(sdfrf)[1]
  FC2 = dim(sdfrf2)[1]
  if (FC > 0)
  {
    dfNU_GVSC$CompletedButOne[i]  = 1; 
    # This vector tells us whether this visitor completed the last but one step of this guide.
  }
  
  if (FC2 > 0)
  {
    dfNU_GVSC$Completed[i]  = 1; 
    # This vector tells us whether this visitor completed this guide.
  }
}

  dfNU_GVSC$StartTime <- as.POSIXct(as.numeric(as.character(dfNU_GVSC$StartTime)),origin="1970-01-01")
  dfNU_GVSC$EndTime <- as.POSIXct(as.numeric(as.character(dfNU_GVSC$EndTime)),origin="1970-01-01")
  dfNU_GVSC$Duration <- (as.numeric(dfNU_GVSC$EndTime)- as.numeric(dfNU_GVSC$StartTime))/60
  
# Percentage matrix
# All of this code is just for assigning the different elements

NPercBuckets <- as.data.frame(matrix(0,numrows,numcols))
colnames(NPercBuckets) <- c("All_Guides","All_Visitors","Num_Steps", "Segment", "Step1", "Step2","Step3","Step4","Step5","Step6","Step7","Step8","Step9","Step10", "Step11","Step12","Step13","Step14","Step15","Step16","Step17","Step18","Step19","Step20", "Step21","Step22")

NPercCBuckets <- as.data.frame(matrix(0,numrows,numcols))
colnames(NPercCBuckets) <- c("All_Guides","All_Visitors","Num_Steps", "Segment","Step1", "Step2","Step3","Step4","Step5","Step6","Step7","Step8","Step9","Step10", "Step11","Step12","Step13","Step14","Step15","Step16","Step17","Step18","Step19","Step20", "Step21", "Step22")

NPercBuckets$All_Guides <- as.character(NBuckets$All_Guides)
NPercBuckets$All_Visitors <- NBuckets$All_Visitors
NPercBuckets$Num_Steps <- NBuckets$Num_Steps
NPercBuckets$Segment <- NBuckets$Segment


NPercCBuckets$All_Guides <- as.character(NBuckets$All_Guides)
NPercCBuckets$All_Visitors <- NBuckets$All_Visitors
NPercCBuckets$Num_Steps <- NBuckets$Num_Steps
NPercCBuckets$Segment <- NBuckets$Segment
NPercCBuckets$Num_Steps <- NBuckets$Num_Steps

dfNU$guideId <- as.character(dfNU$guideId)

# This is the percentage of people who complete each step for this particular guide (all its visitors)
for (i in 1:numrows)
{
  
  nsteps = NPercBuckets$Num_Steps[i]
  ns5 = nsteps+4
  
  NPercBuckets[i,5:ns5] <- 100*(NBuckets[i,5:ns5]/NBuckets$All_Visitors[i])
}


# This is the percentage of people who finish based on the buckets of those who complete each step

for (i in 1:numrows)
{
  
  nsteps = NPercCBuckets$Num_Steps[i]
  ns5 = nsteps+4
  NPercCBuckets[i,5:ns5] <- 100*(NCBuckets[i,5:ns5+1]/NBuckets[i,5:ns5+1])
}
```




```{r, echo=FALSE}
###### REPORTING OF PERCENTAGES #########
# Buildling dataframes for reporting

### This code can be made smarter
NPercBuckets_2 <- subset(NPercBuckets,Num_Steps == 2)
NPercBuckets_3 <- subset(NPercBuckets,Num_Steps == 3)
NPercBuckets_4 <- subset(NPercBuckets,Num_Steps == 4)
NPercBuckets_5 <- subset(NPercBuckets,Num_Steps == 5)
NPercBuckets_6 <- subset(NPercBuckets, Num_Steps == 6)
NPercBuckets_7 <- subset(NPercBuckets, Num_Steps == 7)

NPercCBuckets_2 <- subset(NPercCBuckets,Num_Steps == 2)
NPercCBuckets_3 <- subset(NPercCBuckets,Num_Steps == 3)
NPercCBuckets_4 <- subset(NPercCBuckets,Num_Steps == 4)
NPercCBuckets_5 <- subset(NPercCBuckets,Num_Steps == 5)
NPercCBuckets_6 <- subset(NPercCBuckets, Num_Steps == 6)
NPercCBuckets_7 <- subset(NPercCBuckets, Num_Steps == 7)
### End of comment about smart code
NBuckets$Perc_Completed <- 100.0*(NBuckets$Completed/NBuckets$All_Visitors)

idx_noseg <- which(is.na(NBuckets$Segment))
idx_seg <-  which(!is.na(NBuckets$Segment))

write.csv(dfNU,"dfNU.csv")
write.csv(NBuckets,"NBuckets.csv")
write.csv(NCBuckets,"NCBuckets.csv")
write.csv(NPercBuckets,"NPercBuckets.csv")
write.csv(NVBuckets,"NVBuckets.csv")
write.csv(dfNU_GVSC,"dfNU_GVSC.csv")
write.csv(NPercBuckets,"NPercCBuckets.csv")
```

```{r,echo=FALSE}

#get subset of the data set where numsteps = i
#and then sum up  

```


```{r,echo=FALSE}
#Summarizing percentage completion at each step length

ResAll <- NBuckets[,c("All_Guides","Num_Steps","Perc_Completed")] %>% group_by(Num_Steps) %>% summarize(total_guides = length(All_Guides), perc_completion = mean(Perc_Completed))
ResAll$perc_guides <- 100*ResAll$total_guides/sum(ResAll$total_guides)

#Looking at timings only for instances of completion
ResAll1 <- subset(dfNU_GVSC,Completed == '1') 
ResAll1 <- ResAll1[,c("Guide","Visitor","Num_Steps","Duration")] %>% group_by(Num_Steps) %>% summarize(avg_completion = mean(Duration))

dfNU_GVSC

```

Total guides:
```{r,echo=FALSE}
dim(NBuckets)[1]
```

Average, max and min guide length:
```{r,echo=FALSE}
mean(NBuckets$Num_Steps)
max(NBuckets$Num_Steps)
min(NBuckets$Num_Steps)
```

Visitors:
Total visitors:
```{r,echo=FALSE}
dim(dfNU_GVSC)[1] #includes duplicate visitors across our guides
```
Average, median, min and max number of visitors per guide:
```{r,echo=FALSE}
round(mean(NBuckets$All_Visitors), digits=0)
round(median(NBuckets$All_Visitors), digits=0)
max(NBuckets$All_Visitors)
min(NBuckets$All_Visitors)
```
Unique visitors:
```{r,echo=FALSE}
length(unique(dfNU_GVSC$Visitor))
```

Average, min and max guide length:
```{r,echo=FALSE}
round(mean(NBuckets$Num_Steps), digits=0)
max(NBuckets$Num_Steps)
min(NBuckets$Num_Steps)
```

Based on guideSteps created:
% Tooltip guidesteps:
```{r,echo=FALSE}
dfsteptype <- dfNU[!duplicated(dfNU$guideStepId),]
tooltip = subset(dfsteptype,stepType == 'tooltip')
  100*dim(tooltip)[1]/dim(dfsteptype)[1]
```
% Lightbox guidesteps:
```{r,echo=FALSE}
lightbox = subset(dfsteptype,stepType == 'lightbox')
  100*dim(lightbox)[1]/dim(dfsteptype)[1]
```
% Banner guidesteps:
```{r,echo=FALSE}
banner = subset(dfsteptype,stepType == 'banner')
  100*dim(banner)[1]/dim(dfsteptype)[1]
```

```{r,echo=FALSE}
Guidetypes <- as.data.frame(matrix(0.0,3,3))
factor_not <- c("tooltip","lightbox","banner")
```



```{r,echo=FALSE}
#Distribution of guides by guide length
#

p2 <- ggplot(ResAll,aes(x = Num_Steps , y = total_guides)) 
  p2 + geom_bar(stat = "identity", fill = "#FF4876") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    ggtitle("Distribution of guides by guide length")+
    labs(x="Guide length (steps)", y= "Totals")+
    theme_hc()+
    theme(plot.background = element_rect(fill = "#F6FDFC"))
##barchart(Num_Steps ~ total_guides, data = ResAll, main="Counts of guides by length",ylab="Guide Length",xlab="Counts", col= "##0A817F", border= "white")
```

 

```{r,echo=FALSE}
#Plot of percentage completion at each step length (with size of visitors)

GL1 <- GL[!duplicated(GL$guideId),]
NBuckets1 <- merge(NBuckets, GL1, by.x=c('All_Guides'), by.y=c('guideId'), all.x = TRUE) 

mean(NBuckets1$Perc_Completed)
sum(NBuckets1$All_Visitors)

NBuckets1
write.csv(NBuckets1,"NBuckets1.csv")
```

```{r,echo=FALSE}

library(plotly)
library(ggrepel)
p1 <- ggplot(NBuckets1 ,aes(x = Num_Steps , y = Perc_Completed, , label = paste(name,"[",All_Visitors,"]")))
  p1 + geom_point(aes (size = All_Visitors), colour = "#FF4876") +
    geom_smooth(method= "lm", se = FALSE, colour = "#0A817F") +
    ggtitle("Plot of percentage completion at each step length (trendline)")+
    labs(x="Guide length (steps)", y= "% visitors completed")+
    theme_hc()+
    theme(legend.position="none")+
    theme(plot.background = element_rect(fill = "#F6FDFC"))+
    geom_label_repel(size = 2)
 # p4 <- ggplotly(p1, tooltip = c("text"))

```

No. of guides completed, no. of visitors who completed guides:
```{r,echo=FALSE}
dim(NBuckets[which(NBuckets$Completed!=0),])[1]
sum(NBuckets$Completed) #Metrics for guide length vs average completion time graph -  guides (that were completed by atleast one visitor) and total visitors that completed guides (could have repeats across guides)
```



```{r,echo=FALSE}
#Plot of average completion time at each step length
#library(tidyverse) 
#ResAll1 %>%
   #filter(!is.na(Num_Steps)) %>%
  
ggplot(ResAll1,aes(x = Num_Steps, Hours, y = avg_completion))+
    geom_line(stat = 'identity',color = "#FF4876")+
    geom_smooth(method = "lm", se = FALSE, colour= "#0A817F")+
    labs(x="Guide length (steps)", y= "Average completion time")+
    ggtitle("Plot of average completion time at each step length")+
    theme_hc()+
    theme(legend.position="none")+
    theme(plot.background = element_rect(fill = "#F6FDFC"))
```



Average % of repeat views, repeat visitors per guide:
```{r,echo=FALSE}
#Average %repeatviews and %repeatvisitors by guide length
#dfNU$guideId_visitorId<- paste(dfNU$guideId,dfNU$visitorId)

dfNU$guideStepId_visitorId<- paste(dfNU$guideStepId,dfNU$visitorId)
totalsbyguide <- dfNU[,c("guideId", "numSteps", "guideStepId_visitorId" , "visitorId")] %>% group_by(guideId) %>% summarize(total_views = length(guideStepId_visitorId) , Num_Steps = mean(numSteps), total_visitors = n_distinct(visitorId)) #total views per guide (including duplicates)

repeatviews <- dfNU[duplicated(dfNU$guideStepId_visitorId),]
repeatsbyguide <- repeatviews[,c("guideId", "numSteps", "guideStepId_visitorId", "visitorId")] %>% group_by(guideId) %>% summarize(repeat_views = length(guideStepId_visitorId) , distinct_repeat_views = n_distinct(guideStepId_visitorId), distinct_repeat_visitors = n_distinct(visitorId)) #stepId-visitor combinations repeating more than once - for e.g. for 3 instances of a guideStep-visitorId combo, we count only the repeats i.e. twice)

dfRepeats <- merge(totalsbyguide, repeatsbyguide, by=c('guideId'))
dfRepeats$percent_repeat_views = 100*(dfRepeats$repeat_views/dfRepeats$total_views)
dfRepeats$percent_repeat_visitors = 100*dfRepeats$distinct_repeat_visitors/dfRepeats$total_visitors

mean(dfRepeats$percent_repeat_views)
mean(dfRepeats$percent_repeat_visitors)
dfRepeats <- as.data.frame(dfRepeats)

```


```{r,echo=FALSE}
#Plot of %Repeat views by guide length

dfRepeats <- dfRepeats[,c("Num_Steps", "percent_repeat_views", "percent_repeat_visitors")] %>% group_by(Num_Steps) %>% summarize(percent_repeat_views_by_length = mean(percent_repeat_views), percent_repeat_visitors_by_length = mean(percent_repeat_visitors))

p2 <- ggplot(dfRepeats,aes(x = Num_Steps, Rate, y = percent_repeat_views_by_length))
   p2 + geom_line(stat = 'identity',color = "#FF4876")+
    labs(x="Guide length (steps)", y= "% Repeat views")+
    geom_smooth(method = "lm", se = FALSE, colour= "#0A817F")+
    ggtitle("Plot of % repeat views by guide length")+
    theme_hc()+
    ylim(45,75)+
    theme(legend.position="none")+
    theme(plot.background = element_rect(fill = "#F6FDFC"))
```


```{r,echo=FALSE}
#Plot of %Repeat visitors by guide length

p3 <- ggplot(dfRepeats,aes(x = Num_Steps, Rate, y = percent_repeat_visitors_by_length))
   p3 + geom_line(stat = 'identity',color = "#FF4876")+
    labs(x="Guide length (steps)", y= "% Repeat visitors", na.rm = TRUE)+
    geom_smooth(method = "lm", se = FALSE, colour= "#0A817F")+
    ggtitle("Plot of % repeat visitors by guide length")+
    theme_hc()+
    theme(legend.position="none")+
    theme(plot.background = element_rect(fill = "#F6FDFC"))
```

```{r,echo=FALSE}
#Plot of Walkthrough completion rate (%visitors completed and %of total guides vs guide length)

library(reshape2)
library(ggplot2)
ResAll2<- ResAll[,c("Num_Steps","perc_completion","perc_guides")]
r <- melt(ResAll2, id.vars = 'Num_Steps')

ggplot(r, aes(x=Num_Steps, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+
    ggtitle("Walkthrough completion rate")+
    scale_fill_manual(values = c("#FF4876", "#0A817F"), labels = c("% visitors completed", "% of total guides")) +
    labs(x="Guide length (steps)", y= "%")+
    guides(fill = guide_legend(title = "Legend"))+
    theme_hc()+
    theme(plot.background = element_rect(fill = "#F6FDFC"))
```

```{r,echo=FALSE}
##### ONBOARDING GUIDES AND THEIR EFFECTIVENESS

OBG <- read.csv("/Users/sukmanilamba/Downloads/Onboarding_guides_Pendo.csv")
OBG$Guide_ID <- as.character(OBG$Guide_ID)

dfNU_GVSC_Onb <- subset(dfNU_GVSC,Guide %in% OBG$Guide_ID)

dfNU_GVSC_noseg <- subset(dfNU_GVSC,is.na(Segment))
dfNU_GVSC_seg <- subset(dfNU_GVSC,!is.na(Segment))

dfNU_GVSC_FS <- subset(dfNU_GVSC,FirstStep == 1)

dfNU_GVSC_FS_seg <- subset(dfNU_GVSC_FS,!is.na(Segment))
dfNU_GVSC_FS_noseg <- subset(dfNU_GVSC_FS,is.na(Segment))

dfNU_GVSC_under7 <- subset(dfNU_GVSC,Num_Steps <= 3)
dfNU_GVSC_7plus <- subset(dfNU_GVSC,Num_Steps > 3)

dfNU_GVSC_Onb_noseg <- subset(dfNU_GVSC_Onb,is.na(Segment))
dfNU_GVSC_Onb_seg <- subset(dfNU_GVSC_Onb,!is.na(Segment))

NBuckets_Seg <- subset(NBuckets,!is.na(Segment))
NBuckets_Noseg <- subset(NBuckets,is.na(Segment))
```
Looking at segmentation:

Percentage of users who were not in segments and completed guides:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_noseg$Completed)/dim(dfNU_GVSC_noseg)[1])
```

Percentage of users who were in segments and completed guides:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_seg$Completed)/dim(dfNU_GVSC_seg)[1])
```

Percentage of visitors overall who completed guides:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC$Completed)/dim(dfNU_GVSC)[1])
```
Percentage of visitors overall who completed guides (conditional on completing the first step):
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_FS$Completed)/dim(dfNU_GVSC_FS)[1])
```

Percentage of visitors who completed all except the final step and were not in segments:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_noseg$CompletedButOne)/dim(dfNU_GVSC_noseg)[1])
```

Percentage of visitors who completed all except the final step and were in segments:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_seg$CompletedButOne)/dim(dfNU_GVSC_seg)[1])
```

Percentage of visitors overall who completed all except the final step:
```{r,echo=FALSE}
100*(sum(dfNU_GVSC$CompletedButOne)/dim(dfNU_GVSC)[1])
```

Percentage of visitors overall who completed all except the final step (conditional on finishing the first step):
```{r,echo=FALSE}
100*(sum(dfNU_GVSC_FS$CompletedButOne)/dim(dfNU_GVSC_FS)[1])
```

Onboarding Guides:

```{r,echo=FALSE}
##### ONBOARDING GUIDES AND THEIR EFFECTIVENESS

OBG <- read.csv("/Users/sukmanilamba/Downloads/Onboarding_guides_Pendo.csv")
OBG$Guide_ID <- as.character(OBG$Guide_ID)

dfNU_GVSC_Onb <- subset(dfNU_GVSC,Guide %in% OBG$Guide_ID)

dfNU_GVSC_Onb_noseg <- subset(dfNU_GVSC_Onb,is.na(Segment))
dfNU_GVSC_Onb_seg <- subset(dfNU_GVSC_Onb,!is.na(Segment))

dfNU_GVSC_noseg <- subset(dfNU_GVSC,is.na(Segment))
dfNU_GVSC_seg <- subset(dfNU_GVSC,!is.na(Segment))

dfNU_GVSC_FS <- subset(dfNU_GVSC,FirstStep == 1)

dfNU_GVSC_FS_seg <- subset(dfNU_GVSC_FS,!is.na(Segment))
dfNU_GVSC_FS_noseg <- subset(dfNU_GVSC_FS,is.na(Segment))

dfNU_GVSC_under7 <- subset(dfNU_GVSC,Num_Steps <= 3)
dfNU_GVSC_7plus <- subset(dfNU_GVSC,Num_Steps > 3)

NBuckets_Seg <- subset(NBuckets,!is.na(Segment))
NBuckets_Noseg <- subset(NBuckets,is.na(Segment))

# This is the percentage of users who completed the first walk through 
# For each guide Id
# Get the users who completed all steps
# % of those who completed/all users
# % of those who completed/those who got to first step
# % of those who completed/those who got to first two steps .... 
```










